---
title: "Phoenix Dashboard"
author: Elsa Boardman
format:
  dashboard:
    logo: "https://t3.ftcdn.net/jpg/05/12/88/20/240_F_512882021_fCx3ONBz7fbnR3sqUjhG0RLCEit9CTtA.jpg"
    theme: sketchy
    embed-resources: true
---
# Data

```{r}
#install.packages("DT")
#install.packages("plotly")
library(tidyverse)
library(DT)
library(plotly)
library("ggplot2")
```

```{r}
id <- "1zoYDEdrJoRNTVJXG5BO4ZkSDHWg5XFpG"
phx_dat <- read_csv2(sprintf("https://docs.google.com/uc?id=%s&export=download", id))
```

## Row 1 {height=20%}

::: {.card title="Phoenix Data Information"}
This is a test Quarto Dashboard about data from Phoenix, Arizona
:::

## Row 2 {height=80%}

### Row 2 Column 1
```{r}
#| title: Phoenix Age vs. Car Ownership

plot1 <- phx_dat |>
  ggplot(aes(x = MEDAGE, y = QNOAUTO)) +
  geom_point() +
  labs(
    x = "Age",
    y = "Percent of people who DON'T own cars")

plot1 |> ggplotly ()
```

### Row 2 Column 2

```{r}
#| title: Phoenix Data
phx_dat |> datatable()
```


# Notes


## Row 1 {height=40%}
::: {.card title="About the Author"}
Elsa Boardman made this aweosme Quarto Dashboard. She is a first-year student at University of Washington interested in pursuing Geography and Data science. In her free time, she enjoys dancing, spending quality time with friends/family, and journaling.
:::

## Row 2 {height=60%}
::: {.card titile="Information of the Data Set"}
Phoenix is a car-depended society, so it can be seen in the data how majority of adults do own cars. The percent of people who don't own cars is mostly below 10%. This aligns with the inormation in this article https://www.azfamily.com/2025/10/06/phoenix-metro-ranked-low-walkability-lawmaker-takes-transit-challenge/ which discusses the car-dependence of Phoenix as a whole.
:::



